---
params:
  author: "Maria del Mar Quiroga"
  xlsx: "data/cv.xlsx"
  bib: "data/cv.bib"
title: '`r sprintf("%s - Curriculum Vitæ", params[["author"]])`'
author: '`r params[["author"]]`'
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{css, echo=FALSE}
/* Remove sidebar from second page on 
.pagedjs_page:not(:first-of-type) {*/
.pagedjs_page {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
/* Added to fit all publications in one page, increase substraction to reduce further and delete if no longer needed 
.pagedjs_page:last-of-type .details {
  padding-top: calc(var(--row-blocks-padding-top) - 0.2rem)!important;
} */
/* Remove some extra padding from title to fit first page */
[data-id="title"], [data-id="education"], [data-id="reports"], [data-id="research-and-professional-experience"], [data-id="supervision-and-mentoring"], [data-id="leadership-and-service"], [data-id="awards-and-scholarships"]  {
  margin: 0;
}
.pagedjs_page {
  --pagedjs-margin-top: 0.8in;
  --pagedjs-margin-bottom: 0.8in;
}
```

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("R/cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(data_location = "data/")

#CV$entries_data$description_bullets
```

```{r}
# When in pdf export mode the little dots on the timeline are unaligned, so fix that with some conditional CSS.
cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
```
<!--
# Aside

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
#datadrivencv::build_network_logo(CV$network)
```

## Contact {#contact}

```{r}
CV %>% print_contact_info()
```

## Key skills {#skills}

```{r}
CV %>% print_skill_list(skill_type = "key_skill")
```


## Technical skills
```{r}
CV %>% print_skill_bars(skill_type = "technical", bar_color="#660033")
```

## Disclaimer {#disclaimer}

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown)

Last updated on `r Sys.Date()`
-->
# Main

## Maria del Mar Quiroga {#title}
<!--
```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```
-->
## Education {data-icon="graduation-cap"}

```{r}
CV %<>% print_section('education')
```

## Research and Professional Experience {data-icon="laptop"}

```{r}
CV %<>% print_section('research_positions', glue_template = "academic_cv")
```

## Supervision and Mentoring {data-icon="sitemap"}

```{r}
CV %<>% print_section('supervision_mentoring')
```

## Leadership and Service {data-icon="certificate"}

```{r}
CV %<>% print_section('service')
```

## Awards and Scholarships {data-icon="award"}

```{r}
CV %<>% print_section('awards_scholarships')
```

## Teaching Experience {data-icon="chalkboard-teacher"}

```{r}
CV %<>% print_section('teaching_positions')
```

## Science Communication and Outreach {data-icon="globe"}

```{r}
CV %<>% print_section('outreach')
```

## Professional Development {data-icon="chart-line"}

```{r}
CV %<>% print_section('prof_development')
```

## Journal Articles {data-icon="newspaper"}

```{r}
CV %<>% print_publications(type = "Article")
```

```{r}
CV %<>% print_text_block("articles") 
```

## Reports {data-icon="book"}

```{r}
CV %<>% print_publications(type = "Report")
```

## Book Chapters{data-icon="book"}

```{r}
CV %<>% print_publications(type = "Book chapter")
```

## Preprints {data-icon="newspaper"}

```{r}
CV %<>% print_publications(type = "Preprint")
```

## Software and training material {data-icon="code"}

```{r}
CV %<>% print_publications(type = "Software")
```


## Conference Presentations and Posters {data-icon="image"}

```{r}
CV %<>% print_publications(type = "Conference presentation")
```

## Acknowledged Contributions {data-icon="newspaper"}

```{r}
CV %<>% print_publications(type = "Acknowledgement")
```